---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# PRECISE
## Personalized Integrated Network Modeling
<!-- badges: start -->
<!-- badges: end -->



## Web applet

PRECISE can be used as a web application found at [BayesRx](https://mjha.shinyapps.io/PRECISE/). 


Find out more about the BayesRx group here: [BayesRx Homepage](https://bayesrx.github.io/).

## Installation

This package depends on packages that not are in CRAN. Install these prerequisite packages prior
to installing PRECISE:

``` r
install.packages("BiocManager")
BiocManager::install(c("graph", "RBGL", "BMS"))
```

You can now install PRECISE from [Github](https://github.com/umich-biostatistics/PRECISE) with:

``` r
install.packages("devtools")  # you need devtools to install R packages from Github
devtools::install_github("umich-biostatistics/PRECISE")
```

## Example

```{r example_p1}
library(PRECISE)  # load PRECISE
```

```{r example_p2}
data(rppadat)
RPPAdat = rppadat[[1]] # RPPA data for Apoptosis pathway
p = ncol(RPPAdat)
B = 100
alpha = 0.1
alpha.array = seq(0.0001, 0.1, length = 100) 
#pcfit = fitPC(dat = RPPAdat, alpha = alpha, stable = TRUE, 
#              alpha.array = alpha.array, B = B, labels = as.character(1:p), verbose = T) 
data(pcfit)
pcfit = pcfit.list[[1]] # the fitPC result for Apoptosis pathway 

#  make the results from the ﬁtPC function into weighted adjacency matrix as follows
adj.pc = as(pcfit$fit@graph, "matrix") 
addr = matrix(as.numeric(pcfit$rownames), ncol = 2)
addr.rev = cbind(addr[,2], addr[,1]) 
adj.pc[addr] = adj.pc[addr] * pcfit$pcmaxSel[,1]
adj.pc[addr.rev] = adj.pc[addr.rev] * pcfit$pcmaxSel[,2] 
adj.pc
```

## Getting help

For further illustration of PRECISE, see the vignette included with the package. To see
the available vignettes, use `browseVignettes("PRECISE")`. You can read a specific 
vignette with `vignette(PRECISE)`.

